\href{https://slack.com/}{}

\begin{itemize}
\tightlist
\item
  \href{https://slack.com/is}{Product}
\item
  \href{https://slack.com/pricing?ui_step=55\&ui_element=5}{Pricing}
\item
  \href{https://get.slack.help/hc/en-us}{Support}
\item
  \href{/get}{Download Slack}
\item
  \href{https://slack.com/create}{Create a new workspace}
\item
  \href{https://slack.com/get-started}{Find your workspace}
\item
  \href{https://slack.com/signin}{Sign in}
\item
  \protect\hyperlink{}{Menu}
\end{itemize}

\href{https://slack.com/}{} \protect\hyperlink{}{}

\begin{itemize}
\tightlist
\item
  \href{https://slack.com/is}{Product}
\item
  \href{https://slack.com/pricing?ui_step=55\&ui_element=5}{Pricing}
\item
  \href{https://get.slack.help/hc/en-us}{Support}
\item
  \href{/get}{Download {the Slack app}}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://slack.com/signin}{{Sign in}}
\item
  \href{https://slack.com/create}{{Create a new workspace}}
\end{itemize}

\hypertarget{page}{}
\hypertarget{pageux5fcontents}{}
\emph{} You need to sign in to see this page.

\emph{} \textbf{Too many login failures!}\\
Apologies! There were too many SMS message requests in a short period,
so you'll have to wait a moment to try again.

\emph{} Hmmm\ldots{} something went wrong. Please try again.

\section{\texorpdfstring{Sign in to
{spectroscopy-platform}}{Sign in to spectroscopy-platform}}\label{signinux5fheader}

spectroscopy-platform.slack.com

Enter your \textbf{email address} and \textbf{password}.

What is your \textbf{password}?

{Sign in}

Remember me

\href{/forgot}{Forgot password?} ·
\href{https://slack.com/get-started}{Forgot which email you used?}

\hypertarget{magicux5floginux5fcta}{}
or

\textbf{Long password? Hard to type?}\\
We can email you a magic link so you can sign in without having to type
your password.

Email Me A Link

If you have an \textbf{{ @usys.ethz.ch }} email address, you can
\href{/signup/}{create an account}.

Trying to create a workspace? \href{/create}{Create a new workspace}

\hypertarget{overlay}{}

\begin{itemize}
\tightlist
\item
  Using Slack
\item
  \href{/is}{Product}
\item
  \href{/enterprise}{Enterprise}
\item
  \href{/pricing?ui_step=28\&ui_element=5}{Pricing}
\item
  \href{https://get.slack.help/hc/en-us}{Support}
\item
  \href{/guides}{Slack Guides}
\item
  \href{/apps}{App Directory}
\item
  \href{https://api.slack.com/}{API}
\end{itemize}

\begin{itemize}
\tightlist
\item
  Slack
\item
  \href{/jobs}{Jobs}
\item
  \href{/customers}{Customers}
\item
  \href{/developers}{Developers}
\item
  \href{/events}{Events}
\item
  \href{https://slackhq.com/}{Blog}
\item
  \href{/podcast}{Podcast}
\item
  \href{https://slack.shop/}{Slack Shop}
\end{itemize}

\begin{itemize}
\tightlist
\item
  Legal
\item
  \href{/privacy-policy}{Privacy}
\item
  \href{/security}{Security}
\item
  \href{/terms-of-service}{Terms of Service}
\item
  \href{/policies}{Policies}
\end{itemize}

\begin{itemize}
\tightlist
\item
  Handy Links
\item
  \href{/downloads}{Download desktop app}
\item
  \href{/downloads}{Download mobile app}
\item
  \href{/brand-guidelines}{Brand Guidelines}
\item
  \href{https://slackatwork.com}{Slack at Work}
\item
  \href{https://status.slack.com/}{Status}
\end{itemize}

\href{https://slack.com}{}

\begin{itemize}
\tightlist
\item
  \href{/help/contact}{Contact Us}
\item
  \href{https://twitter.com/SlackHQ}{}
\item
  \href{https://www.youtube.com/channel/UCY3YECgeBcLCzIrFLP4gblw}{}
\end{itemize}
